

```markdown
---
title: "Project Plan for Predicting Exercise Manner Using Accelerometer Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(caret)
library(randomForest)
library(e1071)
```

## 1. Data Understanding and Preparation

### 1.1 Load the Data

```{r load-data}
# Load training and test data
training_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testing_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

training_data <- read.csv(training_url, na.strings = c("NA", "#DIV/0!", ""))
testing_data <- read.csv(testing_url, na.strings = c("NA", "#DIV/0!", ""))
```

### 1.2 Explore the Data

```{r explore-data}
# Check the structure of the datasets
str(training_data)
str(testing_data)

# Summary of training data
summary(training_data)
```

### 1.3 Data Cleaning and Preprocessing

```{r data-cleaning}
# Remove columns with mostly NA values
training_data <- training_data[, colSums(is.na(training_data)) < nrow(training_data) * 0.6]
testing_data <- testing_data[, colSums(is.na(testing_data)) < nrow(testing_data) * 0.6]

# Remove irrelevant columns (e.g., X, user_name, timestamps)
irrelevant_columns <- c("X", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", 
                        "cvtd_timestamp", "new_window", "num_window")
training_data <- training_data %>% select(-one_of(irrelevant_columns))
testing_data <- testing_data %>% select(-one_of(irrelevant_columns))

# Ensure 'classe' is a factor in the training set
training_data$classe <- as.factor(training_data$classe)
```

## 2. Model Building

### 2.1 Split the Training Data

```{r split-data}
set.seed(123)
trainIndex <- createDataPartition(training_data$classe, p = 0.7, 
                                  list = FALSE, 
                                  times = 1)
train_set <- training_data[trainIndex, ]
validation_set <- training_data[-trainIndex, ]
```

### 2.2 Train the Model

```{r train-model}
# Train a Random Forest model
set.seed(123)
rf_model <- randomForest(classe ~ ., data = train_set, importance = TRUE, ntree = 100)

# Print the model summary
print(rf_model)
```

### 2.3 Cross-Validation

```{r cross-validation}
# Perform cross-validation
train_control <- trainControl(method = "cv", number = 5)
rf_cv_model <- train(classe ~ ., data = train_set, method = "rf", trControl = train_control)

# Print the cross-validation results
print(rf_cv_model)
```

## 3. Model Evaluation

### 3.1 Evaluate on Validation Set

```{r evaluate-model}
# Predict on validation set
validation_pred <- predict(rf_model, newdata = validation_set)

# Confusion Matrix
confusionMatrix(validation_pred, validation_set$classe)
```

## 4. Prediction on Test Data

### 4.1 Make Predictions

```{r predict-test-data}
# Make predictions on the test data
test_pred <- predict(rf_model, newdata = testing_data)

# Prepare the submission file
submission <- data.frame(problem_id = testing_data$problem_id, classe = test_pred)
write.csv(submission, file = "submission.csv", row.names = FALSE)
```

## 5. Conclusion

- **Model Selection:** Discuss the choice of the Random Forest model.
- **Model Performance:** Summarize the model performance on the validation set.
- **Future Work:** Suggest potential improvements and future work.

```

Save this template as an `.Rmd` file and open it in RStudio. You can run the code chunks step by step and add your own explanations and interpretations in the markdown sections. Let me know if you need any adjustments or further assistance!

